Network Origins of Social Distinction

### 2025-11-09 manuscript.tex

>>>>

%%% FIGURE 5 KITE GRAPHS
\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/kite.png}
            \caption{Three-Clique/Wheel}
            \label{fig:sf}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/ten-clique-edge.png}
            \caption{Six-Node Wheel}
            \label{fig:sf}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/kite.png}
            \caption{Six-Clique}
            \label{fig:sf}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/ten-clique-edge.png}
            \caption{Ten-Clique}
            \label{fig:sf}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel-clique.png}
            \caption{Three Levels of Hierarchy}
            \label{fig:classicbrokerage3}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel-clique-edge-star.png}
            \caption{Kite Connects to Highest Distinction Node}
            \label{fig:classicbrokerage3}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel-clique-edge-clique.png}
            \caption{Kite Connects to Moderate Distinction Node}
            \label{fig:twoconnected}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel-clique-edge-peri.png}
            \caption{Kite Connects to Lowest Distinction Node}
            \label{fig:circleweld}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/regular-four.png}
            \caption{Kite Connects to Moderate Distinction Node}
            \label{fig:sf}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/regular-edge.png}
            \caption{Kite Connects to Lowest Distinction Node}
            \label{fig:sf}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/regular-four.png}
            \caption{HOLD}
            \label{fig:sf}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/regular-edge.png}
            \caption{HOLD}
            \label{fig:sf}
    \end{subfigure} 
    \caption{Comparison of kite graphs with varying parameters}
\end{figure}
